Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-13 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 While the Global Moran's I could be used with great success to identify the spatial association in smaller areas affected by the virus and help in decision making while dealing with local outbreaks, the LISA would be useful not only to identify with more precision where the spatial association is occurring but it also should be used when the goal is to control Covid-19 outbreaks in larger areas. The Spatio-Temporal Scan Statistic should be used when trying to identify "alive" clusters and their initial date, therefore it would be a great tool in decision making when dealing not only with Covid-19 but with other disease outbreaks.

>>>>

 While the Global Moran's I could be used with great success to identify the spatial association in smaller areas affected by the virus and help in decision making while dealing with local outbreaks, the LISA would be useful not only to identify with more precision where the spatial association is occurring but it also should be used when the goal is to control Covid-19 outbreaks in larger areas. The Spatio-Temporal Scan Statistic should be used when trying to identify "alive" clusters and their initial date, therefore it would be a great tool in decision making when dealing not only with Covid-19 outbreaks but also with other diseases.
